Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-10 paper-kelompok/main.tex
schematics and ack

% Pendahuluan
\section{Introduction}
Currently, various methods detect and measure glucose concentrations in food matrices.
These methods can be broadly grouped into two main categories: enzymatic approaches, such as spectrophotometric assays; and non-enzymatic instrumentation, such as HPLC systems.
While the first group is glucose specific, the latter is broadly adaptable and can be used to detect not only glucose but a wide variety of other carbohydrates as well\cite{b1}.
However, the spectrophotometric test is becoming a more commonly used method for glucose detection because of its ability to detect in a shorter time and at a lower cost.
Spectrophotometric tests utilize the light transmitted or reflected by a sample to perform qualitative and quantitative analysis.
For qualitative analysis, the light transmitted by a sample has a unique spectrum based on the atoms or molecules contained in the sample.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{power-dfd.png}}
    \caption{DFD of the power subsystem}
    \label{power-dfd}
    \end{figure}

@@

\section*{Acknowledgement}

>>>>

% Pendahuluan
\section{Introduction}
Currently, various methods detect and measure glucose concentrations in food matrices.
These methods can be broadly grouped into two main categories: enzymatic approaches, such as spectrophotometric assays; and non-enzymatic approaches, such as HPLC systems.
While the first group is glucose specific, the latter is broadly adaptable and can be used to detect not only glucose but a wide variety of other carbohydrates as well\cite{b1}.
However, the spectrophotometric test is becoming a more commonly used method for glucose detection because of its ability to detect in a shorter time and at a lower cost.
Spectrophotometric tests utilize the light transmitted or reflected by a sample to perform qualitative and quantitative analysis.
For qualitative analysis, the light transmitted by a sample has a unique spectrum based on the atoms or molecules contained in the sample.

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.3]{power-schematic.png}}
    \caption{DFD of the power subsystem}
    \label{power-dfd}
    \end{figure}

@@

\section*{Acknowledgement}
The authors thank Dr. Isa Anshori from Department of Biomedical Engineering, Institut Teknologi Bandung and his research team for assistance with DMF integration and sample preparation.
This work was funded by Department of Electrical Engineering, Institut Teknologi Bandung.
